Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-15 paper.tex
Ask for help?
Proposed a JSON format for AIML. (Blame Alan Kay.)

\begin{figure}\small
\begin{verbatim}
<aiml version="1.0">
<category>
 <pattern>GO *</pattern>
 <template><srai><star/></srai></template>
</category>

<category>
 <pattern>N</pattern>
 <template><srai>NORTH</srai></template>
</category>

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, and \texttt{Go North}. The \texttt{<srai>} tag invokes the
  recognizer recursively.}\label{fig:aiml}
\end{figure}

@@

We are in the process of implementing the Nell system, and expect to
field initial deployments of subsets of Nell in Africa later this year.

>>>>

\begin{figure}\small
\begin{verbatim}
{ aiml: {
  version: "1.0",
  categories: [
    { pattern: "GO *",
      template: "{*}" },
    { pattern: "N",
      template: "{NORTH}" },
    { pattern: "NORTH",
      template: js`FireEvent(Chat, "NORTH")` },
    { pattern: "* THE DOOR",
      template: "{*} DOOR" },
    { pattern: "* SQUEAKY DOOR",
      template: "{*} DOOR" },
    { pattern: "OPEN DOOR",
      template: js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML format has been translated to JSON.
  Template contents in braces invoke the recognizer recursively.
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}

@@

We are in the process of implementing the Nell system, and expect to
field initial deployments of subsets of Nell in Africa later this year.
Volunteer assistance is welcome.
